Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex

Cut, Clue \& Cut~\cite{beier_2014_cvpr} (\textbf{CGC}): We used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
of the original authors.
\textbf{KL}~\cite{Kerninghan-1970}: We use the the  public available 
        implementation 
        \footlabel{opengm-master}{%
        %\footnote{
        %    \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified

    version of a public available implementation implementation \footref{opengm-master}.

    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{itemize}
And the following proposed solvers:
\begin{itemize}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
\end{itemize}

@@

As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.

@@

For 2D images, we took the models from \cite{andres_2011_iccv}
which are defined on the images of the Berkeley Segmentation
Database \cite{martin_2001}.
For 3D volume segmentation we took the models from
Andres \etal \cite{kroeger_2012_eccv}.
We use models with the cube sizes $150^3$, $300^3$, $450^3$, $550^3$ and $900^3$.
Both, the 2D and 3D models are available in a recent graphical model
benchmark of Kappes \etal ~\cite{kappes_2013_benchmark_cvpr}.
We use the same names for the datasets as in the benchmark,
\emph{image-seg} for the models from  \cite{andres_2011_iccv} and \emph{knott-150 - knott-550} and \emph{3d-seg}
for the models from \cite{kroeger_2012_eccv}.
The size of instances is given in tab. ~\ref{tab:instance_sizes}.

\begin{table}[H]
   \tiny
   \centering
   \caption{Datasets used for evaluation}
   \label{tab:instance_sizes}
   \begin{tabular}{llllc}
      \toprule
         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
      \midrule 
         image-seg        &     156-3764        & ???        & 100          & $\bullet$    \\ 
         knott-150        &     572-972         & ???        & 2            & $\times$ \\
         knott-300        &     3846 - 5896     & ???        & 2            & $\times$ \\
         knott-450        &     15150-17070     & ???        & 2            & $\times$ \\
         knott-550        &     27286 - 31249   & ???        & 2            & $\times$ \\
         3d-seg           &     7958 - 101220   & ???        & 2            & $\times$ \\
         slashdot         &     ???             & ???        & ???          & $\times$ \\     
      \bottomrule
   \end{tabular}
\end{table}

>>>>

For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
Secondly, we follow~\cite{kroeger_2012_eccv}. and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
during the separation procedure.
This procedure is one magnitude faster, but might cause a few extra outer iterations.
In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempinsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.

As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
Therefore we exclude those in our experiments.

We compare this methods to the following methods suggested in the present paper.
%
Energy Based Based Hierarchical Clustering (\textbf{EHC})
as described in sec.~\ref{sec:ehc}.
%
CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
%
The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
 and MC-I and CGC as subproblem solvers denoted by 
\textbf{fusionCC-HC-MC},
\textbf{fusionCC-HC-CGC},
\textbf{fusionCC-WS-MC}, and 
\textbf{fusionCC-WS-CGC}, respectively.
We set the size of the proposals fix to $10\%$ of the original problem size
and the standard derivation of the random edge noise to $1.5$.

@@

@@

For 2D images, we took the models from \cite{andres_2011_iccv}
which are defined on the images of the Berkeley Segmentation
Database \cite{martin_2001}.
For 3D volume segmentation we took the models from
Andres \etal \cite{kroeger_2012_eccv}.
We use models with the cube sizes $150^3$, $300^3$, $450^3$, $550^3$ and $900^3$.
Both, the 2D and 3D models are available in a recent graphical model
benchmark of Kappes \etal~\cite{kappes_2013_benchmark_cvpr}.
We use the same names for the datasets as in the benchmark,
\emph{image-seg} for the models from  \cite{andres_2011_iccv} and \emph{knott-150 - knott-550} and \emph{3d-seg}
for the models from \cite{kroeger_2012_eccv}.
The size of instances is given in Tab.~\ref{tab:instance_sizes}.

\begin{table}[H]
   \tiny
   \centering
   \caption{Datasets used for evaluation}
   \label{tab:instance_sizes}
   \begin{tabular}{llllc}
      \toprule
         Dataset          &     \#Nodes     & \#Edges  & \#Instances  & Planar        \\ 
      \midrule 
         image-seg        &     156-3764        & ???        & 100          & $\bullet$    \\ 
         knott-150        &     572-972         & ???        & 2            & $\times$ \\
         knott-300        &     3846 - 5896     & ???        & 2            & $\times$ \\
         knott-450        &     15150-17070     & ???        & 2            & $\times$ \\
         knott-550        &     27286 - 31249   & ???        & 2            & $\times$ \\
         3d-seg           &     101220   & ???        & 1            & $\times$ \\
         slashdot         &     ???             & ???        & ???          & $\times$ \\     
      \bottomrule
   \end{tabular}
\end{table}

\begin{table}[H]
   \tiny
   \centering
   \caption{Eval}
   \label{tab:eval}
   \begin{tabular}{lllllll}
      \toprule
         Dataset          &  image-seg &  knott-3d-150 &knott-3d-300 &knott-3d-450 &knott-3d-550 &3d-seg\\
      \midrule 
         PIVOT-BOEM       &      \\ 
         HC               &\\
         HC-CGC           &    \\
         CGC              &   \\
         KL               & \\
         FUSION           &  \\
         MC-R             &  \\   
         MC-I             &  \\  
         FusionCC-HC-MC   &  \\  
         FusionCC-HC-CGC  &  \\  
         FusionCC-WS-MC   &  \\  
         FusionCC-WS-CGC  &  \\      
      \bottomrule
   \end{tabular}
\end{table}
